---
title: "Sleep analysis student wellness group"
author: "Rajnish Kumar"
date: "2024-05-13"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(Matrix)
library(lme4)
library(lme4)
library(lmerTest)
library(ggplot2)
```

Sleep analysis on student wellness group

```{r}
df_sleep <-read.csv('C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Documents\\Student Wellness Dataset\\student_wellness_sleep_details.csv')
df_MOOD <- read.csv('C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Documents\\Student Wellness Dataset\\df_MOOD_SWG.csv')
```

```{r}
#df_ONC <-read.csv('C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Desktop\\steps_onc.csv', nrows = 10)
```


```{r}
df_MOOD <- df_MOOD[df_MOOD$MOOD != 0, ]
df_MOOD <- df_MOOD %>% rename(SLEEP_DATE = METRIC_START_DATE) # So that I can join two data frames later. 
# df_MOOD_sleep <- merge(df_sleep, df_MOOD, by = c("STUDY_PRTCPT_ID", "SLEEP_DATE"), all = FALSE)

```


```{r}
# Define sleep variables
sleep_vars <- c('ASLEEP_VALUE', 'INBED_VALUE', 'DEEP_MIN', 'DEEP_COUNT', 'LIGHT_MIN', 'LIGHT_COUNT', 
                'REM_MIN', 'REM_COUNT', 'WAKE_MIN', 'WAKE_COUNT', 'ASLEEP_MIN', 'ASLEEP_COUNT', 
                'AWAKE_COUNT', 'AWAKE_MIN', 'RESTLESS_COUNT', 'RESTLESS_MIN')

v <- colSums(is.na(df_sleep[, sleep_vars]))
v <- names(v[v < 500])

vv <- c("STUDY_PRTCPT_ID", "SLEEP_START_DATE", "SLEEP_END_DATE", "SLEEP_DATE", v)
dx <- df_sleep[, vv, drop = FALSE]

```


```{r}
dx$YEARDAY <- yday(as.Date(dx$SLEEP_DATE))
dx$DAYOFWEEK <- wday(as.Date(dx$SLEEP_DATE), label = FALSE) - 1  # Adjust if week start is Sunday in the given dataset

# Helper function to calculate hours since midnight
hours_since_midnight <- function(time) {
  hour(time) + minute(time) / 60 + second(time) / 3600
}

# Calculate time-related features
dx$SLEEP_START_TIME <- hours_since_midnight(dx$SLEEP_START_DATE)
dx$SLEEP_END_TIME <- hours_since_midnight(dx$SLEEP_END_DATE)

# Apply trigonometric transformations
dx$SLEEP_START_SIN <- sin(2 * pi * dx$SLEEP_START_TIME / 24)
dx$SLEEP_START_COS <- cos(2 * pi * dx$SLEEP_START_TIME / 24)
dx$SLEEP_END_SIN <- sin(2 * pi * dx$SLEEP_END_TIME / 24)
dx$SLEEP_END_COS <- cos(2 * pi * dx$SLEEP_END_TIME / 24)
dx$YEARDAY_SIN <- sin(2 * pi * dx$YEARDAY / 366)
dx$YEARDAY_COS <- cos(2 * pi * dx$YEARDAY / 366)
```



```{r}
# Calculate STUDYDAY
dx <- dx %>%
  group_by(STUDY_PRTCPT_ID) %>%
  mutate(STUDYDAY = YEARDAY - min(YEARDAY)) %>%
  ungroup()

# Drop unused columns
#dx <- dx %>% select(-c(SLEEP_START_DATE, SLEEP_END_DATE, SLEEP_START_TIME, SLEEP_END_TIME, SLEEP_DATE))
dx <- dx %>% select(-c(SLEEP_START_DATE, SLEEP_END_DATE, SLEEP_START_TIME, SLEEP_END_TIME))


dx <- na.omit(dx) # Dropping rows with NA values

colnames(dx) # Print remaining column names

```


```{r}
df_MOOD_sleep_polar <- merge(dx, df_MOOD, by = c("STUDY_PRTCPT_ID", "SLEEP_DATE"), all = FALSE)
df_MOOD_sleep_polar <- df_MOOD_sleep_polar%>% select(-c('STUDY_METRIC_AGGREGATE_ID','METRIC_END_DATE','X','METRIC_END_DATE','STUDY_ID'))
```


```{r}
columns_for_norm <- c('ASLEEP_VALUE', 'INBED_VALUE', 'DEEP_MIN', 'DEEP_COUNT', 
                      'LIGHT_MIN', 'LIGHT_COUNT', 'REM_MIN', 'REM_COUNT', 
                      'WAKE_MIN', 'WAKE_COUNT', 'STEP_COUNT', 'SLEEP_COUNT')

df_MOOD_sleep_polar_MOOD_NZ_norm <- df_MOOD_sleep_polar

df_MOOD_sleep_polar_MOOD_NZ_norm[columns_for_norm] <- as.data.frame(lapply(df_MOOD_sleep_polar[columns_for_norm],function(x) {(x - mean(x)) / sd(x)}))

```

INBED_VALUE = ASLEEP_VALUE + WAKE_MIN         # This is not true for only two cases for df_MOOD_sleep_polar  
abc <- df_sleep$ASLEEP_VALUE + df_sleep$WAKE_MIN - df_sleep$INBED_VALUE # mostly 0's and NA's 
df_sleep$ASLEEP_VALUE - df_sleep$DEEP_MIN - df_sleep$LIGHT_MIN - df_sleep$REM_MIN                    # This is also mostly 0's and NA's,  THIS IS TYPE == STEAGES
df_sleep$ASLEEP_VALUE + df_sleep$WAKE_MIN - df_sleep$INBED_VALUE                                     # This is also mostly 0's and NA's   THIS IS TYPE == STAGES  


## Including Plots

You can also embed plots, for example:

```{r}
df_sleep_classic <- subset(df_sleep, TYPE == "classic")
df_sleep_stages <- subset (df_sleep, TYPE == "stages")
```

df_sleep_classic$ASLEEP_MIN - df_sleep_classic$ASLEEP_VALUE          # This is all 0's for classic stages. 
df_sleep_classic$ASLEEP_VALUE + df_sleep_classic$AWAKE_MIN + df_sleep_classic$RESTLESS_MIN- df_sleep_classic$INBED_VALUE    # Mostly 0's except a very few. 

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
# df_sleep_classic$SLEEP_START_DATE  <-as.POSIXct(df_sleep_classic$SLEEP_START_DATE, format = "%Y-%m-%d %H:%M:%S")
# df_sleep_classic$SLEEP_END_DATE <-as.POSIXct(df_sleep_classic$SLEEP_END_DATE, format = "%Y-%m-%d %H:%M:%S")
# df_sleep_stages$SLEEP_START_DATE  <-as.POSIXct(df_sleep_stages$SLEEP_START_DATE, format = "%Y-%m-%d %H:%M:%S")
# df_sleep_stages$SLEEP_END_DATE <-as.POSIXct(df_sleep_stages$SLEEP_END_DATE, format = "%Y-%m-%d %H:%M:%S")

```

```{r}
# time_diff_classic <- df_sleep_classic$SLEEP_START_DATE - df_sleep_classic$SLEEP_END_DATE
# time_diff_stages <- df_sleep_stages$SLEEP_START_DATE - df_sleep_stages$SLEEP_END_DATE
```

```{r}
# classic_stages_common_days <- intersect(df_sleep_classic$SLEEP_DATE, df_sleep_stages$SLEEP_DATE)
# print(classic_stages_common_days)
```

participant W7LX2I74  has lots of measurements of sleep. 

```{r}
# df_sleep_classic_W7LX2I74 <- df_sleep_classic%>% filter(STUDY_PRTCPT_ID=='W7LX2I74')
# df_sleep_stage_W7LX2I74 <- df_sleep_stages %>% filter(STUDY_PRTCPT_ID=='W7LX2I74')
# common_classis_stages_W7LX2I74 <- intersect(df_sleep_classic_W7LX2I74$SLEEP_DATE, df_sleep_stage_W7LX2I74$SLEEP_DATE)
```
This confirms that on same night, participants can have both types (classic and stages).

Doing prediction of MOOD from "stages" type of sleep. 

```{r}
model <- lmer(MOOD ~ SLEEP_END_SIN + SLEEP_END_COS + DEEP_MIN + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)

summary(model)
confint(model)
par(mfrow=c(2,2))
plot(model)
residuals4 <- residuals(model)
fitted_values <- fitted(model)
```
```{r}

```

          
 mixed effect model to predict MOOD where the predictors are SLEEP_END_SIN and DEEP_MIN, and random effect is given by STUDY_PRTCPT_ID

```{r}
# Alternatively, you can create each diagnostic plot separately:
# Residuals vs Fitted
plot(residuals(model) ~ fitted(model))
abline(h = 0, col = "red")

# Histogram of Residuals
hist(residuals(model), breaks = "FD", main = "Histogram of Residuals")

# Q-Q Plot of Residuals
qqnorm(residuals(model))
qqline(residuals(model), col = "red")

# Scale-Location Plot (Spread vs Level)
plot(fitted(model), scale(residuals(model)), main = "Scale-Location Plot")
abline(h = 0, col = "red")
```


```{r}
library(ggplot2)

# Extracting random effects
re <- ranef(model)$STUDY_PRTCPT_ID

# Adding participant ID as a column
re$ID <- rownames(re)

# Basic random effects plot
ggplot(re, aes(x = ID, y = `(Intercept)`)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  xlab("Participant ID") +
  ylab("Random Intercept")

# Alternatively, you can use `dotplot` from `lattice` package
library(lattice)
dotplot(ranef(model, condVar = TRUE))
```

```{r}
# Assuming that MOOD is a column in your data frame with actual values
df_MOOD_sleep_polar_MOOD_NZ_norm$predicted_MOOD <- predict(model, re.form = NA)

ggplot(df_MOOD_sleep_polar_MOOD_NZ_norm, aes(x = MOOD, y = predicted_MOOD)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red") +
  xlab("Actual MOOD") +
  ylab("Predicted MOOD") +
  ggtitle("Predicted vs Actual MOOD Values")
```


```{r}
model_lm <- lm( formula = MOOD ~ SLEEP_END_SIN  + SLEEP_END_COS + DEEP_MIN , data = df_MOOD_sleep_polar_MOOD_NZ_norm)

summary(model_lm)
par(mfrow=c(2,2))
plot(model_lm)
residuals4 <- residuals(model_lm)
fitted_values <- fitted(model_lm)
```


```{r}
model1 <- lmer(MOOD ~ SLEEP_COUNT + STEP_COUNT + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)

summary(model1)
confint(model1)
# par(mfrow=c(2,2))
# plot(model1)
# residuals4 <- residuals(model1)
# fitted_values <- fitted(model1)


```


```{r}
model_upto_2_interact <- lmer(MOOD ~ (DEEP_MIN + LIGHT_MIN + REM_MIN + WAKE_MIN)^2 + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model_upto_2_interact)
confint(model_upto_2_interact)

# par(mfrow=c(2,2))
# plot(model_upto_2_interact)
# residuals_upto_2_interact <- residuals(model_upto_2_interact)
# fitted_values_upto_2_interact <- fitted(model_upto_2_interact)

```

```{r}
model_upto_2_interact_selected <- lmer(MOOD ~ (LIGHT_MIN + WAKE_MIN )^2 + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model_upto_2_interact_selected)
confint(model_upto_2_interact_selected)
```


```{r}
model_upto_2_interact_selected <- lmer(MOOD ~ (DEEP_MIN + REM_MIN )^2 + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model_upto_2_interact_selected)
confint(model_upto_2_interact_selected)
```


```{r}
model_upto_2_interact_selected <- lmer(MOOD ~ (DEEP_MIN + REM_MIN + ASLEEP_VALUE)^2 + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model_upto_2_interact_selected)
confint(model_upto_2_interact_selected)
```
```{r}
model_upto_2_interact_selected <- lmer(MOOD ~ (DEEP_MIN + REM_MIN + ASLEEP_VALUE + SLEEP_START_SIN + SLEEP_START_COS + STEP_COUNT)^2 + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model_upto_2_interact_selected)
confint(model_upto_2_interact_selected)
```
```{r}
model_upto_2_interact_selected <- lmer(MOOD ~ (DEEP_MIN + REM_MIN +  SLEEP_START_SIN + SLEEP_START_COS)^2 + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model_upto_2_interact_selected)
confint(model_upto_2_interact_selected)
```


```{r}
# Alternatively, you can create each diagnostic plot separately:
# Residuals vs Fitted
plot(residuals(model1) ~ fitted(model1))
abline(h = 0, col = "red")

# Histogram of Residuals
hist(residuals(model1), breaks = "FD", main = "Histogram of Residuals")

# Q-Q Plot of Residuals
qqnorm(residuals(model1))
qqline(residuals(model1), col = "red")

# Scale-Location Plot (Spread vs Level)
plot(fitted(model1), scale(residuals(model1)), main = "Scale-Location Plot")
abline(h = 0, col = "red")
```



```{r}
model2 <- lmer(MOOD ~  SLEEP_COUNT + STEP_COUNT + (1 | DAYOFWEEK), data = df_MOOD_sleep_polar_MOOD_NZ_norm)

summary(model2)
confint(model2)
plot(model2)
```


```{r}

# Assuming that MOOD is a column in your data frame with actual values
df_MOOD_sleep_polar_MOOD_NZ_norm$predicted_MOOD <- predict(model2, re.form = NA)

ggplot(df_MOOD_sleep_polar_MOOD_NZ_norm, aes(x = MOOD, y = predicted_MOOD)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red") +
  xlab("Actual MOOD") +
  ylab("Predicted MOOD") +
  ggtitle("Predicted vs Actual MOOD Values")


```
```{r}
# Alternatively, you can create each diagnostic plot separately:
# Residuals vs Fitted
plot(residuals(model2) ~ fitted(model2))
abline(h = 0, col = "red")

# Histogram of Residuals
hist(residuals(model2), breaks = "FD", main = "Histogram of Residuals")

# Q-Q Plot of Residuals
qqnorm(residuals(model2))
qqline(residuals(model2), col = "red")

# Scale-Location Plot (Spread vs Level)
plot(fitted(model2), scale(residuals(model2)), main = "Scale-Location Plot")
abline(h = 0, col = "red")
```




```{r}
model3 <- lmer(MOOD ~ DEEP_MIN + STEP_COUNT + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)

summary(model3)
confint(model3)
```


```{r}
model4 <-lm(formula = MOOD ~ DEEP_MIN + LIGHT_MIN + REM_MIN + WAKE_MIN, data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model4)
par(mfrow=c(2,2))
plot(model4)
residuals4 <- residuals(model4)
fitted_values <- fitted(model4)
```



```{r}
model4_mem <-lmer(MOOD ~ DEEP_MIN + LIGHT_MIN + REM_MIN + WAKE_MIN + (1 | STUDY_PRTCPT_ID),    data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model4_mem)
#plot(model4_mem)
```
```{r}
model4_mem_interact <- lmer(MOOD ~ DEEP_MIN + LIGHT_MIN + REM_MIN + WAKE_MIN + DEEP_MIN:REM_MIN + LIGHT_MIN:WAKE_MIN +
                         (1 | STUDY_PRTCPT_ID),data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model4_mem_interact)
#plot(model4_mem_interact)

```

```{r}

```



```{r}
library(lmerTest)
# df_MOOD_sleep_polar_MOOD_NZ_norm$total_sleep_step <-df_MOOD_sleep_polar_MOOD_NZ_norm$SLEEP_COUNT * df_MOOD_sleep_polar_MOOD_NZ_norm$STEP_COUNT
# 
# model5 <- lmer(MOOD ~ DEEP_MIN + total_sleep_step + (1 | DAYOFWEEK), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
# 
# summary(model5)
```
```{r}
# df_MOOD_sleep_polar_mul <- df_MOOD_sleep_polar
# df_MOOD_sleep_polar_mul$total_sleep_step  <- df_MOOD_sleep_polar_mul$ SLEEP_COUNT * df_MOOD_sleep_polar_mul$STEP_COUNT
# columns_norm <- c('ASLEEP_VALUE', 'INBED_VALUE', 'DEEP_MIN', 'DEEP_COUNT', 
#                       'LIGHT_MIN', 'LIGHT_COUNT', 'REM_MIN', 'REM_COUNT', 
#                       'WAKE_MIN', 'WAKE_COUNT', 'STEP_COUNT', 'SLEEP_COUNT', 'MOOD', 'total_sleep_step')
# 
# df_MOOD_sleep_polar_mul_norm <- df_MOOD_sleep_polar_mul
# 
# df_MOOD_sleep_polar_mul_norm[columns_norm] <- as.data.frame(lapply(df_MOOD_sleep_polar_mul_norm[columns_norm], function(x) {
#   (x - mean(x)) / sd(x)


```

```{r}
# Fit the linear mixed effects model
model6 <- lmer(MOOD ~ SLEEP_COUNT + STEP_COUNT + (1 + DAYOFWEEK| STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model6)

```
```{r}
model7_a <- lmer(MOOD ~ ASLEEP_VALUE + WAKE_MIN + WAKE_COUNT + SLEEP_START_SIN + SLEEP_START_COS + STEP_COUNT + SLEEP_COUNT + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model7_a)
confint(model7_a)

```



```{r}
model7 <- lmer(MOOD ~ DEEP_MIN + STEP_COUNT + (1 + DEEP_MIN + STEP_COUNT | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)

summary(model7)
confint(model7)
```


```{r}
model8 <- lmer(MOOD ~  ASLEEP_VALUE * WAKE_MIN * WAKE_COUNT * SLEEP_START_SIN * SLEEP_START_COS*    STEP_COUNT * SLEEP_COUNT + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model8)
confint(model8)
```

```{r}
model9 <- lmer(MOOD ~  ASLEEP_VALUE * SLEEP_START_SIN * SLEEP_START_SIN* STEP_COUNT  + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model9)
confint(model9)

```


```{r}
model12 <- lmer(MOOD ~  ASLEEP_VALUE * DEEP_MIN *  STEP_COUNT  + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model12)
confint(model12)
```


```{r}
model13 <- lmer(MOOD ~  DEEP_MIN *  STEP_COUNT  + (1 | STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model13)
confint(model13)
```


```{r}
model13 <- lmer(MOOD ~  DEEP_MIN *  STEP_COUNT  + (1 + STEP_COUNT| STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model13)
confint(model13)
```


```{r}
model13 <- lmer(MOOD ~  DEEP_MIN *  STEP_COUNT  + (1 + DEEP_MIN| STUDY_PRTCPT_ID), data = df_MOOD_sleep_polar_MOOD_NZ_norm)
summary(model13)
confint(model13)
```

