---
title: "SWG_regression_models"
author: "Rajnish Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Do the following regression models as starting point. These are all for the prediction of daily MOOD score. 
  Demographics only, 

Demographics plus the following: 
1. resting heart rate 
2. mean, 
3. standard deviation == mode 4 
4. demographic plus mean
5. demographics plus standard deviations. 

6. MOOD 

amount of time in mode 5, 6, and 7. 

steps counts in 5, 6, and 7. 

percentage of minutes out of 24 hours. 

```{r}
# Data Reading & Manipulation
library(tidyr)
library(dplyr)
library(data.table)
library(lubridate)
library(tidyverse)
library(dplyr)

# Data Visualization
library(viridis)  # For better color palettes
library(hrbrthemes)  # For theme_ipsum()
library(plotly)  # For interactive plots
library(gtsummary)
```


Calculate summary statistics for heart rates and steps for the student wellness group. 

```{r }
df_SWG_all <- readRDS("df_COMB_SWG_all_20250110_1248.rds")
roadmap_IDs <- read.csv("C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Documents\\Analysis_projects_R_laptop\\SWG_R_project\\SWG_data\\StudentWellness_RoadmapID.csv")
dev_IDs <- read.csv("C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Documents\\Analysis_projects_R_laptop\\SWG_R_project\\SWG_data\\Device_ID.csv")

```



```{r}
roadmap_IDs$onboard_date <- as.Date(roadmap_IDs$onboard_date, format="%m/%d/%y")

length_of_study <- 119                                                     # Make it 89 or 119 based on the feedbacks. 
roadmap_IDs$day_0 <- as.Date(roadmap_IDs$onboard_date, format="%m/%d/%y")
roadmap_IDs$day_last <- roadmap_IDs$day_0 + length_of_study

```

Import MOOD data set and demography, then do the regression models on MOOD and demography. 

Make sure to filter the mood according to the study period and filter out the data outside the study period. 

```{r}
df_MOOD_time <- read.csv("C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Documents\\Analysis_projects_R_laptop\\SWG_R_project\\SWG_data\\SWG_mood_time_entry.csv")

df_MOOD_time <- df_MOOD_time[df_MOOD_time$INT_SRVY_RSPNS!="SELECTED",]
```




```{r}
library(dplyr)
library(lubridate)

library(dplyr)
library(lubridate)

df_MOOD <- df_MOOD_time %>%
  mutate(
    MOOD_report_date = as.Date(gsub("^(\\d{4}-\\d{2}-\\d{2}).*$", "\\1", INT_SRVY_RSPNS_DT))
  ) %>%
  select(
    MOOD_report_date,
    INT_SRVY_RSPNS,
    STUDY_PRTCPT_ID
  )

df_MOOD<- df_MOOD%>%mutate(INT_SRVY_RSPNS = as.numeric(INT_SRVY_RSPNS))
```

Filter out the date range for MOOD score. 

```{r}
library(dplyr)

df_MOOD_120 <- df_MOOD %>%
  left_join(roadmap_IDs, by = c("STUDY_PRTCPT_ID" = "rm_access_code")) %>%
   filter(MOOD_report_date >= day_0 & MOOD_report_date <= day_last) %>%
  select(MOOD_report_date, INT_SRVY_RSPNS, STUDY_PRTCPT_ID)

```



```{r}
library(readxl)
SWG_demo <- read_excel("C:\\Users\\rajnishk\\OneDrive - Michigan Medicine\\Documents\\Analysis_projects_R_laptop\\SWG_R_project\\SWG_data\\Student Wellness Demographics.xlsx")
```



```{r}
filtered_SWG_demo <- SWG_demo %>%
  filter(`Study ID` %in% c("Age", "Female" , "Male" ))
```



```{r}
filtered_SWG_demo_no_identity <- filtered_SWG_demo %>%
  select(-Identity)
```



```{r}
library(tidyr)
transposed_demo <- as.data.frame(t(filtered_SWG_demo_no_identity))
names(transposed_demo) <- transposed_demo[1,]
transposed_demo <- transposed_demo[-1,]
```

Removing the row with "Total" value 
```{r}
transposed_demo <- transposed_demo[-nrow(transposed_demo), ]
```


```{r}
demographic_SWG_final <- transposed_demo
demographic_SWG_final <- demographic_SWG_final%>% mutate(Age = as.numeric(Age))

demographic_SWG_final <- demographic_SWG_final %>%
  mutate(
    Sex = case_when(
      Male == "x" ~ "male",
      Female == "x" ~ "female",
      TRUE ~ NA_character_
    )
  )


```
Match it with the roadmap IDs and start and end date of the study. 

```{r}
library(dplyr)
roadmap_IDs_with_demographics <- roadmap_IDs %>%
  left_join(demographic_SWG_final %>% 
              mutate(study_id = rownames(demographic_SWG_final)), 
            by = "study_id")
```


```{r}
# write.csv(roadmap_IDs_with_demographics, file = "roadmap_IDs_with_demographics.csv", row.names = FALSE)
```



Filter the mood data frame with the range of study dates present in roadmap_IDs_with_demographics along with add demographic information to be able to implement some regression models. 


```{r}
library(dplyr)

df_MOOD_120_with_demographics <- df_MOOD_120 %>%
  left_join(
    roadmap_IDs_with_demographics %>% 
    select(rm_access_code, Age, Sex),
    by = c("STUDY_PRTCPT_ID" = "rm_access_code")
  )
```


```{r}
# library(dplyr)
# 
# df_MOOD_120_with_demographics <- df_MOOD_120_with_demographics %>%
#   mutate(
#     Sex = case_when(
#       Male == "x" ~ "male",
#       Female == "x" ~ "female",
#       TRUE ~ NA_character_
#     )
#   )
```


Let us do several regression models with demographics only. 

```{r}
# df_MOOD_120_with_demographics$Sex <- as.factor(df_MOOD_120_with_demographics$Sex)

```

The data frame going into regression model will be called df_regression and will be derived right before the model statement to keep the code smooth.

```{r}
df_regression <- df_MOOD_120_with_demographics[!is.na(df_MOOD_120_with_demographics$Age), ] # There are no missing values in Age. 

library(lmerTest)
library(performance)
model1 <- lmer(INT_SRVY_RSPNS ~ Age + (1 | STUDY_PRTCPT_ID), data = df_regression)


```



```{r}
df_regression <- df_MOOD_120_with_demographics[!is.na(df_MOOD_120_with_demographics$Age), ]
# df_regression[df_regression$Age>25,]$Age <- 25
df_regression[df_regression$Age>25,]$Age <- 25
model1a <- lmer(INT_SRVY_RSPNS ~ Age + Sex + (1 | STUDY_PRTCPT_ID), data = df_regression)

```



```{r}

df_regression <- df_MOOD_120_with_demographics[!is.na(df_MOOD_120_with_demographics$Sex), ]
model2 <- lmer(INT_SRVY_RSPNS ~ Sex + (1 | STUDY_PRTCPT_ID), data = df_regression)
```



```{r}
# df_regression same as before

model3 <- lmer(INT_SRVY_RSPNS ~ Age + Sex + (1 | STUDY_PRTCPT_ID), data = df_regression)

```


```{r}
# df_regression same as before
model4 <- lmer(INT_SRVY_RSPNS ~ Age * Sex + (1 | STUDY_PRTCPT_ID), data = df_regression)


```


```{r}
model5 <- lmer(INT_SRVY_RSPNS ~ Age + Sex + (Age | STUDY_PRTCPT_ID), data = df_regression)

```
```{r}
model6 <- lmer(INT_SRVY_RSPNS ~ Age * Sex + (Age + Age:Sex | STUDY_PRTCPT_ID), data = df_regression)

``` 
Get the physiological data and include it here. 



```{r}
library(data.table)
library(moments) 

setDT(df_SWG_all)  

all_participants_SWG_stats <- df_SWG_all[
  HR_msrd_Y_N == 1 & ACTIVITY_TYPE_VAL != 0,
  .(
    # HR statistics
    hr_mean = mean(HR_MSRMNT_VAL, na.rm = TRUE),
    hr_sd = sd(HR_MSRMNT_VAL, na.rm = TRUE),
    hr_skewness = skewness(HR_MSRMNT_VAL, na.rm = TRUE),
    hr_kurtosis = kurtosis(HR_MSRMNT_VAL, na.rm = TRUE),
    
    # Steps statistics
    steps_sum = sum(STEPS_MSRMNT_VAL, na.rm = TRUE),
    steps_mean = mean(STEPS_MSRMNT_VAL, na.rm = TRUE),
    steps_sd = sd(STEPS_MSRMNT_VAL, na.rm = TRUE),
    steps_skewness = skewness(STEPS_MSRMNT_VAL, na.rm = TRUE),
    steps_kurtosis = kurtosis(STEPS_MSRMNT_VAL, na.rm = TRUE),
    
    n_observations = .N
  ),
  by = .(prtcpt_id, day, ACTIVITY_TYPE_VAL)
]
```


Removing type 4 where there is steps count

```{r}
all_participants_SWG_stats_type_4_filtered <- all_participants_SWG_stats %>% 
  filter(!(ACTIVITY_TYPE_VAL == 4 & steps_sum != 0))
```

Get the data frame for participant - day with all the stats. 


```{r}
HR_STEPS_filtered_stats_SWG_all_ptcpt <- all_participants_SWG_stats_type_4_filtered %>%
  pivot_wider(
    id_cols = c(prtcpt_id, day),
    names_from = ACTIVITY_TYPE_VAL,
    names_glue = "{.value}_type_{ACTIVITY_TYPE_VAL}",
    values_from = c(hr_mean, hr_sd, hr_skewness, hr_kurtosis, 
                   steps_sum, steps_mean, steps_sd, 
                   steps_skewness, steps_kurtosis, n_observations)
  )
```

Add the information about date for each of the participant-day combination.Tehn you can add demographic information and do regression models again.

```{r}
# Map the date for participant-day
date_mapping <- df_SWG_all[, .(date = as.Date(msmt_instant)[1]), by = .(prtcpt_id, day)]
```

Combine the dates with the stats of physiological data HR_STEPS_filtered_stats_SWG_all_ptcpt

```{r}
HR_STEPS_filtered_stats_SWG_all_ptcpt <- HR_STEPS_filtered_stats_SWG_all_ptcpt %>%
  left_join(date_mapping, by = c("prtcpt_id", "day"))
```

Combine HR_STEPS_filtered_stats_SWG_all_ptcpt with demography and MOOD, so that you can do regression with demography, physiological data and MOOD. 


```{r}
library(dplyr)

df_HR_STEPS_stats_demo_MOOD_120 <- HR_STEPS_filtered_stats_SWG_all_ptcpt %>% 
  left_join(df_MOOD_120_with_demographics %>% 
      select(STUDY_PRTCPT_ID, MOOD_report_date, INT_SRVY_RSPNS),
    by = c(
      "prtcpt_id" = "STUDY_PRTCPT_ID",
      "date" = "MOOD_report_date"
    )
  )

# This data set df_HR_STEPS_stats_demo_MOOD_120 represents days for which we have both physiological signals as well as self reported MOOD. There are a few days, where fitbit data is not present but MOOD score is present. 

# Add the demographic values to it 

library(dplyr)

# First, get unique participant-demographic pairs
participant_demographics <- roadmap_IDs_with_demographics %>%
  select(rm_access_code , Age, Sex) %>%
  distinct()

# Now join this with your main dataframe
df_HR_STEPS_stats_demo_MOOD_120 <- df_HR_STEPS_stats_demo_MOOD_120 %>%
  left_join(
    participant_demographics,
    by = c("prtcpt_id" = "rm_access_code")
  )
```



Add total number of minutes of observations for each participant day. It might introduce NAs to some rows for total_wear_time, because one of the types of activities might be NA value for that person-day. 



```{r}
df_HR_STEPS_stats_demo_MOOD_120 <- df_HR_STEPS_stats_demo_MOOD_120%>%
                     mutate(total_wear_time = n_observations_type_5+ n_observations_type_6+ n_observations_type_4+ n_observations_type_7 )

```




We can try several regression models now. Make sure to create a df_regression data frame that keeps information about the data set used in immediate model. 

```{r}
library(lmerTest)
library(performance)

df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Age, Sex, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4)

  )

# Basic model with all predictors
model7 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4 + Age + Sex + (1 | prtcpt_id), data = df_regression, na.action = na.omit)


```


```{r}
# Basic model with all predictors

df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4,  Sex, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4)

  )

model8 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + Sex + (1 | prtcpt_id), data = df_regression, na.action = na.omit)

```


```{r}
# attach(mtcars)
plot(df_regression$hr_mean_type_4, df_regression$hr_sd_type_4, main="Scatterplot Example",
   xlab="mean", ylab="sd ", pch=19)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4,  INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4)

  )
model9 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, steps_sum_type_7,n_observations_type_7, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7)
  )
model10 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, Age, Sex, hr_sd_type_4, steps_sum_type_7,n_observations_type_7, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7)
  )
model10 <- lmer(INT_SRVY_RSPNS ~ Age + Sex +  n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}
# attach(mtcars)
plot(df_regression$n_observations_type_7, df_regression$hr_sd_type_4, main="Scatterplot Example",
   xlab=" obs time of type 7", ylab=" sedentary HR STD ", pch=19)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_7,n_observations_type_7, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7)
  )
model11 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + Age+ Sex+ n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_7,n_observations_type_7,total_wear_time, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7),
    total_wear_time     = scale(total_wear_time)    
  )
model12 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + Age+ Sex+ total_wear_time + n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date,  hr_sd_type_4, Sex, Age, steps_sum_type_7,n_observations_type_7,total_wear_time, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
   
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7),
    total_wear_time     = scale(total_wear_time)    
  )
model13 <- lmer(INT_SRVY_RSPNS ~  hr_sd_type_4  + steps_sum_type_7 + Age+ Sex+ total_wear_time + n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_7,steps_sd_type_7, n_observations_type_7,total_wear_time, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7),
    steps_sd_type_7 = scale(steps_sd_type_7),
    total_wear_time     = scale(total_wear_time)    
  )
model14 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sd_type_7+ Age+ Sex+ total_wear_time + n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```


```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, Sex, Age, steps_sum_type_7,steps_sd_type_7, n_observations_type_7,total_wear_time, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7),
    steps_sd_type_7 = scale(steps_sd_type_7),
    total_wear_time     = scale(total_wear_time)    
  )
model15 <- lmer(INT_SRVY_RSPNS ~ steps_sum_type_7 + steps_sd_type_7+ Age+ Sex+ total_wear_time + n_observations_type_7 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```


```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_6, steps_sum_type_7, n_observations_type_6, n_observations_type_7,total_wear_time, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7),
    steps_sum_type_6 = scale(steps_sum_type_6),
    total_wear_time     = scale(total_wear_time)    
  )
model16 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sum_type_6 + Age+ Sex+ total_wear_time + n_observations_type_7 + n_observations_type_6 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```


```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_6, steps_sum_type_7, n_observations_type_6, n_observations_type_7, INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    n_observations_type_7 = scale(n_observations_type_7),
    steps_sum_type_6 = scale(steps_sum_type_6)
      
  )
model17 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sum_type_6 + Age+ Sex+  n_observations_type_7 + n_observations_type_6 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```


```{r}
model18 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sum_type_6 + Age* Sex+  n_observations_type_7 + n_observations_type_6 + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```



```{r}

df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_6, steps_sum_type_7,   INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_7 = scale(steps_sum_type_7),
    steps_sum_type_6 = scale(steps_sum_type_6)
      
  )


model19 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sum_type_6 + Age* Sex + (hr_sd_type_4 | prtcpt_id), data = df_regression, na.action = na.omit)
```


```{r}
df_regression <- df_HR_STEPS_stats_demo_MOOD_120 %>% 
                         select(prtcpt_id, date, hr_mean_type_4, hr_sd_type_4, Sex, Age, steps_sum_type_6, steps_sum_type_5,steps_sum_type_7,   INT_SRVY_RSPNS  )

df_regression <- df_regression %>%
  mutate(
    hr_mean_type_4 = scale(hr_mean_type_4),
    hr_sd_type_4 = scale(hr_sd_type_4),
    steps_sum_type_5 = scale(steps_sum_type_5),
    steps_sum_type_7 = scale(steps_sum_type_7),
    steps_sum_type_6 = scale(steps_sum_type_6)
      
  )


model20 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sum_type_5 + steps_sum_type_6 + Age* Sex + (hr_sd_type_4 | prtcpt_id), data = df_regression, na.action = na.omit)
```


```{r}
model21 <- lmer(INT_SRVY_RSPNS ~ hr_mean_type_4 + hr_sd_type_4  + steps_sum_type_7 + steps_sum_type_5 + hr_sd_type_4*steps_sum_type_6 + Age* Sex + (1 | prtcpt_id), data = df_regression, na.action = na.omit)
```


Following is just for the sanity check. All these pairs should represent same participants and their sex. 
```{r}
df_MOOD_demo_pair <- df_MOOD_120_with_demographics%>%select(STUDY_PRTCPT_ID,Sex)%>%distinct()

roadmap_demo_pair <- roadmap_IDs_with_demographics%>% select(rm_access_code,Sex)%>% distinct()

HR_STEPS_stats_demo_pair <- df_HR_STEPS_stats_demo_MOOD_120 %>% select(prtcpt_id,Sex)%>% distinct()


print("entire code ran successfully")

```



```{r}

```

